Towards Comparable Active Learning

### 2023-05-19 doc/al_benchmark_paper.tex
typiclust bugfix normalized embeddings

\begin{table}[]
	\begin{tabular}{l|lll}
		& Splice        & DNA           & USPS          \\
		\hline
		Oracle          & 0.835 $\pm$ 0.01 & 0.879 $\pm$ 0.01 & 0.870 $\pm$ 0.01 \\
		SAL\_23\_01\_16 & 0.808 $\pm$ 0.01 & 0.857 $\pm$ 0.02 & 0.865 $\pm$ 0.01 \\
		Coreset\_Greedy & 0.808 $\pm$ 0.01 & 0.853 $\pm$ 0.02 & 0.849 $\pm$ 0.01 \\
		MarginScore     & 0.806 $\pm$ 0.01 & 0.855 $\pm$ 0.02 & 0.864 $\pm$ 0.01 \\
		ShannonEntropy  & 0.808 $\pm$ 0.01 & 0.855 $\pm$ 0.02 & 0.864 $\pm$ 0.01 \\
		RandomAgent     & 0.797 $\pm$ 0.01 & 0.823 $\pm$ 0.02 & 0.831 $\pm$ 0.01
	\end{tabular}
\end{table}
%
\begin{table}[]
	\begin{tabular}{l|ll}
		& Cifar10 & FashionMnist \\
		\hline
		Oracle          & 0.718 $\pm$ 0.01  & 0.721 $\pm$ 0.01       \\
		SAL\_23\_01\_16 & 0.660 $\pm$ 0.01  & 0.667 $\pm$ 0.01       \\
		Coreset\_Greedy & 0.668 $\pm$ 0.01  & 0.674 $\pm$ 0.01       \\
		MarginScore     & 0.674 $\pm$ 0.01  & 0.677 $\pm$ 0.01       \\
		ShannonEntropy  & 0.671 $\pm$ 0.01  & 0.680 $\pm$ 0.01       \\
		RandomAgent     & 0.632 $\pm$ 0.02  & 0.633 $\pm$ 0.01      
	\end{tabular}
\end{table}
%
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\linewidth]{img/eval_splice_embedded}
	\caption{Results for all algorithms on the pre-encoded Splice dataset}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.8\linewidth]{img/eval_splice_embedded_cd}
\caption{Critical Difference Diagram for Splice where every restart of the algorithm is one sample for the Wilcoxon-Holm method}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.8\linewidth]{img/eval_macro}
\caption{Critical Difference Diagram for Splice, DNA, USPS and Cifar10}
\end{figure}

@@

>>>>

\begin{table}[]
	\begin{tabular}{l|lll}
		& Splice        & DNA           & USPS          \\
		\hline
		Oracle          & 0.830 +- 0.01 & 0.836 +- 0.02 & 0.823 +- 0.01 \\
		SAL & 0.799 +- 0.01 & 0.797 +- 0.03 & 0.809 +- 0.01 \\
		Coreset & 0.800 +- 0.01 & 0.795 +- 0.03 & 0.787 +- 0.02 \\
		TypiClust       & 0.790 +- 0.01 & 0.771 +- 0.04 & 0.761 +- 0.02 \\
		MarginScore     & 0.797 +- 0.02 & 0.795 +- 0.04 & 0.808 +- 0.01 \\
		ShannonEntropy  & 0.799 +- 0.02 & 0.794 +- 0.04 & 0.807 +- 0.01 \\
		RandomAgent     & 0.788 +- 0.01 & 0.765 +- 0.03 & 0.772 +- 0.01 \\
		Badge           & 0.807 +- 0.01 & 0.769 +- 0.06 & 0.797 +- 0.02 \\
		BALD            & 0.811 +- 0.01 & 0.743 +- 0.04 & 0.717 +- 0.05
	\end{tabular}
	\caption{AUC values for all algorithms on the tabular datasets. Higher is better.}
\end{table}
%
\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{img/eval_dna}
	\caption{Results for all algorithms on the DNA dataset}
\end{figure}
%
\begin{figure}
\centering
	\includegraphics[width=0.8\linewidth]{img/macro_al.png}
	\caption{Critical Difference Diagram for all datasets and algorithms}
\end{figure}

@@

\section{Other result tables}
\begin{table}[H]
	\begin{tabular}{l|lll}
		& SpliceEncoded & DNAEncoded    & USPSEncoded   \\
		\hline
		Oracle          & 0.754 +- 0.02 & 0.726 +- 0.02 & 0.674 +- 0.01 \\
		SAL & 0.675 +- 0.03 & 0.640 +- 0.04 & 0.634 +- 0.01 \\
		Coreset & 0.690 +- 0.02 & 0.644 +- 0.05 & 0.607 +- 0.02 \\
		TypiClust       & 0.695 +- 0.02 & 0.660 +- 0.03 & 0.643 +- 0.01 \\
		MarginScore     & 0.675 +- 0.03 & 0.643 +- 0.05 & 0.632 +- 0.02 \\
		ShannonEntropy  & 0.673 +- 0.03 & 0.638 +- 0.05 & 0.626 +- 0.02 \\
		RandomAgent     & 0.680 +- 0.03 & 0.633 +- 0.04 & 0.594 +- 0.02 \\
		Badge           & 0.670 +- 0.04 & 0.600 +- 0.07 & 0.597 +- 0.02 \\
		BALD            & 0.660 +- 0.04 & 0.597 +- 0.06 & 0.652 +- 0.01
	\end{tabular}
	\caption{AUC values for all algorithms on the encoded tabular datasets. Higher is better.}
\end{table}
%
\begin{table}[H]
	\begin{tabular}{l|ll}
		& Cifar10Encoded & FashionMnistEncoded \\
		\hline
		Oracle          & 0.699 +- 0.01  & 0.721 +- 0.01       \\
		SAL & 0.623 +- 0.01  & 0.667 +- 0.01       \\
		Coreset & 0.641 +- 0.01  & 0.674 +- 0.01       \\
		TypiClust       & 0.627 +- 0.01  & 0.638 +- 0.01       \\
		MarginScore     & 0.641 +- 0.01  & 0.676 +- 0.01       \\
		ShannonEntropy  & 0.637 +- 0.02  & 0.680 +- 0.01       \\
		RandomAgent     & 0.598 +- 0.02  & 0.633 +- 0.01       \\
		Badge           & 0.645 +- 0.02  & 0.681 +- 0.01       \\
		BALD            & 0.633 +- 0.01  & 0.666 +- 0.01      
	\end{tabular}
	\caption{AUC values for all algorithms on the encoded image datasets. Higher is better.}
\end{table}
%
\begin{table}[H]
	\begin{tabular}{l|ll}
		& TopV2         & News          \\
		\hline
		Oracle          & 0.860 +- 0.01 & 0.448 +- 0.01 \\
		SAL & 0.831 +- 0.01 & 0.312 +- 0.01 \\
		Coreset & 0.816 +- 0.02 & 0.355 +- 0.02 \\
		TypiClust       & 0.718 +- 0.02 & 0.314 +- 0.01 \\
		MarginScore     & 0.821 +- 0.02 & 0.357 +- 0.01 \\
		ShannonEntropy  & 0.794 +- 0.02 & 0.342 +- 0.01 \\
		RandomAgent     & 0.776 +- 0.02 & 0.349 +- 0.01 \\
		Badge           & 0.824 +- 0.01 & 0.343 +- 0.01 \\
		BALD            & 0.825 +- 0.02 & 0.347 +- 0.01
	\end{tabular}
\caption{AUC values for all algorithms on the text datasets. Higher is better.}
\end{table}
